---
title: "Analysis"
author: "Jesper Fischer Ehmsen"
date: "`r Sys.Date()`"
output: html_document
---

# This is the markdown for reproducing the analyses and results of the paper titled "Assessing Individual Sensitivity to the Thermal Grill Illusion: A Two-Dimensional Adaptive Psychophysical Approach" 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(ggplot2, tidyverse, DHARMa, glmmTMB, reshape, gamlss, scales)
```

## Load the data:
```{r}
source(here::here("scripts","Utility_functions.R"))

df = prep_data(per_threshold = F)

```



### Here, you can access to the models directly, avoiding the need to rerun them, which can save considerable time.
```{r}
load(here::here("Workspace","supplementary_workspace.RData"))
```


## Reliable calibration of the Thermal Grill Illusion across individuals

### Cold Ratings
```{r}

dfcold = df %>% dplyr::select(ID, Trial_N, Quartile, Burning_prob, Stim_dur, experiment, VAS_Cold, Stimulus,Location) %>% 
  mutate(Location = as.factor(Location))


dfcold$Stimulus = relevel(dfcold$Stimulus, ref = "TGI")

## Due to singular convergence have to not include regressors on 0's

main_cold <- gamlss(VAS_Cold ~ Stimulus * Burning_prob + Quartile + Trial_N + Stim_dur + re(random = ~ 1 | experiment/ID), #+vasReactionTime_Cold
           nu.formula = ~1 + re(random = ~ 1 |  experiment/ID),#1,
           tau.formula = ~ 1 + re(random = ~ 1 |  experiment/ID),#1, 
           sigma.formula = ~1 + Stimulus * Burning_prob + Quartile + Trial_N + Stim_dur + re(random = ~ 1 |  experiment/ID),
           data = dfcold,
           family = BEINF(mu.link = "logit",sigma.link = "logit",nu.link = "logit",tau.link = "logit"),
           control = gamlss.control(n.cyc = 50, trace = F))

summary(main_cold)

# Statistics for manuscript
stats_main_cold <- summary_stats_zoib_new(main_cold, coefficients = 8, round = 2, part = "mu")

# Simulated residuals:
plot(main_cold)
```

### Warm Ratings
```{r}

dfwarm = df %>% dplyr::select(ID, Trial_N, Quartile, Burning_prob,Stim_dur, experiment, VAS_Warm, Stimulus,Location)%>% 
  mutate(Location = as.factor(Location))

dfwarm$Stimulus = relevel(dfwarm$Stimulus, ref = "TGI")

main_warm <- gamlss(VAS_Warm ~ Stimulus * Burning_prob + Quartile + Trial_N + Stim_dur + re(random = ~ 1 | experiment/ID), #+vasReactionTime_Cold
           nu.formula = ~ Stimulus * Burning_prob + Quartile + Trial_N + Stim_dur + re(random = ~ 1 |  experiment/ID),#1,
           tau.formula = ~ 1 + re(random = ~ 1 |  experiment/ID),#1, 
           sigma.formula = ~ Stimulus * Burning_prob + Quartile + Trial_N + Stim_dur + re(random = ~ 1 | experiment/ID),
           data = dfwarm,
           family = BEINF(mu.link = "logit",sigma.link = "logit",nu.link = "logit",tau.link = "logit"),
           control = gamlss.control(n.cyc = 50, trace = F))

summary(main_warm)
  
# Statistics for manuscript
stats_main_warm <- summary_stats_zoib_new(main_warm, coefficients = 8, round = 2, part = "mu")

# Simulated residuals:
plot(main_warm)

```

### Burning Ratings
```{r}

dfburn = df %>% dplyr::select(ID, Trial_N, Quartile, Burning_prob, Stim_dur, experiment, VAS_Burn, Stimulus, Location)%>% 
  mutate(Location = as.factor(Location))

dfburn$Stimulus = relevel(dfburn$Stimulus, ref = "TGI")


main_burn<- gamlss(VAS_Burn ~ Stimulus * Burning_prob + Quartile + Trial_N + Stim_dur + re(random = ~ 1 | experiment/ID), #+vasReactionTime_Cold
           nu.formula = ~ Stimulus * Burning_prob + Quartile + Trial_N + Stim_dur + re(random = ~ 1 |  experiment/ID),#1,
           tau.formula = ~ 1 + re(random = ~ 1 |  experiment/ID),#1, 
           sigma.formula = ~1 + Stimulus * Burning_prob + Quartile + Trial_N + Stim_dur + re(random = ~ 1 |  experiment/ID),
           data = dfburn,
           family = BEINF(mu.link = "logit",sigma.link = "logit",nu.link = "logit",tau.link = "logit"),
           control = gamlss.control(n.cyc = 50, trace = F))

summary(main_burn)

# Statistics for manuscript
stats_main_burn <- summary_stats_zoib_new(main_burn, coefficients = 8, round = 2, part = "mu")

# Simulated residuals:
plot(main_burn)
```

# Thermosensory index
```{r}
# Testing the quality of the sensation

# Normalized difference
df$coldwarm_ratio <- df$VAS_Cold / (df$VAS_Cold + df$VAS_Warm)

df_coldwarm <- df%>% dplyr::select(coldwarm_ratio, Burning_prob, Quartile, Trial_N, Stim_dur, ID, Stimulus,experiment,Location) %>% drop_na() %>% 
  mutate(Location = as.factor(Location))

df_coldwarm$Stimulus = relevel(df_coldwarm$Stimulus, ref = "TGI")

main_sensation <- gamlss(coldwarm_ratio ~  Burning_prob + Quartile * Stimulus + Trial_N + Stim_dur + re(random = ~ 1 |  experiment/ID),
           nu.formula = ~ Stimulus + re(random = ~ 1 |  ID),
           tau.formula = ~ Stimulus + re(random = ~ 1 |  ID),
           sigma.formula = ~  Burning_prob + Quartile * Stimulus + Trial_N + Stim_dur + re(random = ~ 1 |  experiment/ID),
           data = df_coldwarm,
           family = BEINF(mu.link = "logit",sigma.link = "logit",nu.link = "logit",tau.link = "logit"),
           control = gamlss.control(n.cyc = 50, trace = T))

# Summary of the regression
summary(main_sensation)

# Statistics for manuscript
stats_main_sensation <- summary_stats_zoib_new(main_sensation, coefficients = 10, round = 2, part = "mu")

# Simulated residuals:
plot(main_sensation)


```

# Getting the data from the TGIF for reporting
```{r, fig.height=6, fig.width=8}
alldata <- read.csv(here::here("data","fastTrl.csv")) 

#parameter means and standard erros:
parameters = c("t0","t30","alpha","S")
errors = paste0(parameters, "_se")

#getting the means (last trial of PSI)
q = alldata %>% 
  dplyr::group_by(sub) %>% 
  summarize(lastS = last(S), lastt0 = last(t0), lastt30 = last(t30), lastalpha = last(alpha)) %>% 
  pivot_longer(cols = paste0("last",parameters), values_to = "mean_values", names_to = "parameters")

#getting the standard errors (last trial of PSI)
q_se = alldata %>% 
  dplyr::group_by(sub) %>% 
  summarize(lastS_se = last(S_se), lastt0_se = last(t0_se), lastt30_se = last(t30_se), lastalpha_se = last(alpha_se)) %>% 
  pivot_longer(cols = paste0("last",parameters,"_se"), values_to = "se_values", names_to = "parameters") %>% mutate(parameters = str_remove(parameters, "_se"))

#combine
vals = inner_join(q,q_se)


# for each parameter we do bootstrapping to get real group level estiamtes:
params_df = data.frame()

for(parameter in parameters){
  
  #get the right parameter:
  parameter = paste0("last",parameter)
  
  #Lazy way of no error propergation:
  without_error_prop = vals %>% filter(parameters == parameter) %>% summarize(mean = mean(mean_values), sd = sd(mean_values))
  
  #with:
  with_error_prop = vals %>% filter(parameters == parameter) %>% rowwise() %>% 
    mutate(new_mean = list(rnorm(10000,mean_values, se_values))) %>% 
    unnest() %>% summarize(mean = mean(new_mean), sd = sd(new_mean))
  
  #save data.
  params_df = rbind(params_df,without_error_prop %>% mutate(error_prop = "F", parameters = parameter))
  params_df = rbind(params_df,with_error_prop %>% mutate(error_prop = "T", parameters = parameter))
}

# Plotting to demonstrate: the difference
vals %>% mutate(error_prop = NA) %>% ggplot()+
  geom_pointrange(aes(x = sub, y = mean_values, ymin = mean_values - 2 * se_values, ymax = mean_values + 2 * se_values))+
  facet_wrap(~parameters, scales = "free")+
  geom_pointrange(data = params_df, aes(x = 0, y = mean, ymin = mean - 2 * sd, ymax = mean + 2 * sd, col = error_prop), position = position_dodge(width = 3), alpha = 1)


# saving only the error proporgation
TGIF_parameters = params_df %>% filter(error_prop == "T")
```

# Cold pain thresholds
```{r, fig.height=6, fig.width=8}

# Same as for TGI parameters now for cold and heat pain thresholds:
alldata <- read.csv(here::here("data","psi.csv")) %>% filter(quality == "cold")

parameters = c("threshold","slope")
errors = paste0(parameters, "_se")


q = alldata %>% 
  dplyr::group_by(sub) %>% 
  summarize(lastthreshold = last(threshold), lastslope = last(slope)) %>% 
  pivot_longer(cols = paste0("last",parameters), values_to = "mean_values", names_to = "parameters")


q_se = alldata %>% 
  dplyr::group_by(sub) %>% 
  summarize(lastthreshold_se = last(threshold_se), lastslope_se = last(slope)) %>% 
  pivot_longer(cols = paste0("last",parameters,"_se"), values_to = "se_values", names_to = "parameters") %>% mutate(parameters = str_remove(parameters, "_se"))


vals = inner_join(q,q_se)

vals %>% ggplot(aes(x = sub, y = mean_values, ymin = mean_values-2*se_values,ymax = mean_values+2*se_values))+geom_pointrange()+facet_wrap(~parameters, scales = "free")


params_df = data.frame()

for(parameter in parameters){
  parameter = paste0("last",parameter)
  
  without_error_prop = vals %>% filter(parameters == parameter) %>% summarize(mean = mean(mean_values), sd = sd(mean_values))
  
  with_error_prop = vals %>% filter(parameters == parameter) %>% rowwise() %>% 
    mutate(new_mean = list(rnorm(10000,mean_values, se_values))) %>% 
    unnest() %>% summarize(mean = mean(new_mean), sd = sd(new_mean))

  params_df = rbind(params_df,without_error_prop %>% mutate(error_prop = "F", parameters = parameter))
  
  params_df = rbind(params_df,with_error_prop %>% mutate(error_prop = "T", parameters = parameter))
  
}


vals %>% mutate(error_prop = NA) %>% ggplot()+
  geom_pointrange(aes(x = sub, y = mean_values, ymin = mean_values - 2 * se_values, ymax = mean_values + 2 * se_values))+
  facet_wrap(~parameters, scales = "free")+
  geom_pointrange(data = params_df, aes(x = 0, y = mean, ymin = mean - 2 * sd, ymax = mean + 2 * sd, col = error_prop), position = position_dodge(width = 3), alpha = 1)


#save in a dataframe
cold_painthresholds = params_df %>% filter(error_prop == "T")
```


# heat pain thresholds
```{r, fig.height=6, fig.width=8}
alldata <- read.csv(here::here("data","psi.csv")) %>% filter(quality == "warm")

parameters = c("threshold","slope")
errors = paste0(parameters, "_se")


q = alldata %>% 
  dplyr::group_by(sub) %>% 
  summarize(lastthreshold = last(threshold), lastslope = last(slope)) %>% 
  pivot_longer(cols = paste0("last",parameters), values_to = "mean_values", names_to = "parameters")


q_se = alldata %>% 
  dplyr::group_by(sub) %>% 
  summarize(lastthreshold_se = last(threshold_se), lastslope_se = last(slope)) %>% 
  pivot_longer(cols = paste0("last",parameters,"_se"), values_to = "se_values", names_to = "parameters") %>% mutate(parameters = str_remove(parameters, "_se"))



vals = inner_join(q,q_se)

vals %>% ggplot(aes(x = sub, y = mean_values, ymin = mean_values - 2 * se_values, ymax = mean_values + 2 * se_values)) +
  geom_pointrange() + 
  facet_wrap(~parameters, scales = "free")

params_df = data.frame()

for(parameter in parameters){
  parameter = paste0("last",parameter)
  
  without_error_prop = vals %>% filter(parameters == parameter) %>% summarize(mean = mean(mean_values), sd = sd(mean_values))
  
  with_error_prop = vals %>% filter(parameters == parameter) %>% rowwise() %>% 
    mutate(new_mean = list(rnorm(10000,mean_values, se_values))) %>% 
    unnest() %>% summarize(mean = mean(new_mean), sd = sd(new_mean))

  params_df = rbind(params_df,without_error_prop %>% mutate(error_prop = "F", parameters = parameter))
  
  params_df = rbind(params_df,with_error_prop %>% mutate(error_prop = "T", parameters = parameter))
  
}

vals %>% mutate(error_prop = NA) %>% ggplot()+
  geom_pointrange(aes(x = sub, y = mean_values, ymin = mean_values - 2 * se_values, ymax = mean_values + 2 * se_values))+
  facet_wrap(~parameters, scales = "free") +
  geom_pointrange(data = params_df, aes(x = 0, y = mean, ymin = mean - 2 * sd, ymax = mean + 2 * sd, col = error_prop), position = position_dodge(width = 3), alpha = 1)

heat_painthresholds = params_df %>% filter(error_prop == "T")
```


# getting the proportion of 0 and 1's in the data in each of the 3 qualities. Here i've a function makes sense as there are 6 combinations
```{r}
prop_0_cold = get_prop(0, df,quality = "Cold")*100
prop_1_cold = get_prop(1, df,quality = "Cold")*100

prop_0_warm = get_prop(0, df,quality = "Warm")*100
prop_1_warm = get_prop(1, df,quality = "Warm")*100

prop_0_burn = get_prop(0, df,quality = "Burn")*100
prop_1_burn = get_prop(1, df,quality = "Burn")*100
```


# Now we save the results for the manuscript! 

```{r Saving reporting statistics}
# Get a list of all variable names that start with "stats_"
stats_vars <- ls(pattern = "^stats_")

props <- ls(pattern = "^prop_")

# # Combine the variable names into a single vector
vars_to_save <- c(stats_vars, props, "TGIF_parameters", "heat_painthresholds", "cold_painthresholds")
#
# # Save the variables to a file
base::save(list = vars_to_save, file = here::here( "Workspace", "reporting_statistics.RData"))

```

# Now we save the results for the supplemenary material!

```{r Saving variables / models To run Supplementary analysis alone}

# Combine the variable names into a single vector
vars_to_save <- c(
  "main_warm", "dfwarm",
  "main_cold", "dfcold",
  "main_burn", "dfburn",
  "main_sensation","df_coldwarm"
)

# Save the variables to a file
base::save(list = vars_to_save, file = here::here( "Workspace", "supplementary_workspace.RData"),compress = "xz")
```
